SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-30 docs/questioning.tex
some corrections

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail. A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject JavaScript code
into the page to steal the user's cookie for this particular
page and send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
code fragment to the malicious web site:

\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
\begin{lstlisting}
<iframe style="position:absolute;top:-9999px"
    src="http://foo.net/vulnerable.html?query=
    <script>document.write(
    '<img src=\"http://malicious.com/?c=
    '+encodeURIComponent(document.cookie)+'\">')
    </script>"></iframe>
\end{lstlisting}

\noindent
By using the {\tt iframe} tag, the web user will not
realise the redirection. 
This problem is actually solved by the architectures
presented in Subsubsection~~\ref{sec:mashups}.

>>>>

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail. A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject an {\tt iframe}
into the page to steal the user's cookie and
send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
link to the malicious web site (or send it via phishing)
and induce the user to click on it:

\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
\begin{lstlisting}
http://foo.net/vulnerable.html?query=
<iframe src="javascript:document.body.innerHTML=+
'<img src=\"http://malicious.com/?c=
'+encodeURIComponent(document.cookie)+'\">'">
</iframe>
\end{lstlisting}

\noindent
{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
can actually detect such an attack (along with some architectures
presented in Subsubsection~~\ref{sec:mashups}).
To achieve this, {\sc soma} requires site administrators
to specify legitimate, external domains for sending
or receiving information in order to approve interactions
between them and the protected web site.
